---
title: "Does Sleep Causally affect Stress?"
subtitle: "CME Assignment II"
author: "Rishabh Patil | 2021A7PS0464H"
layout: page
output:
  pdf_document: 
    includes:
      in_header: "wrap-code.tex"
    toc: yes
    fig_caption: yes
    number_sections: yes
    keep_tex: yes
    highlight: espresso
    fig_crop: no
  html_document: 
    toc: yes
    highlight: textmate
    theme: simplex
    fig_width: 10
    fig_height: 7
    fig_caption: yes
  html_notebook: 
    toc: yes
    highlight: espresso
    theme: united
    fig_caption: yes
    number_sections: yes
editor_options:
  chunk_output_type: inline
  markdown: 
    wrap: 72
---

```{r LaTex Wrap, include=FALSE}
knitr::opts_chunk$set(tidy.opts = list(width.cutoff = 60), tidy = TRUE)
```

```{r}
library(readr)
```

# Research Question

*Primary question:* Does Sleep Stress Levels of Students? We will study
the data collected from various volunteers and analyze the causal
relation between sleep an stress.

*Hypothesis:* Lower hours of sleep and lower sleep quality leads to high
stress levels.

The data we use has:

1.  Anxiety Level (GAD-7)

2.  Self Esteem (Rosenberg Self Esteem Scale)

3.  Mental Health History (0-1)

4.  Depression(in accordance with PHQ-9)

5.  Headache

6.  [*Sleep Quality*]{.underline} [treatment 1]

7.  Basic Needs

8.  Blood Pressure(low)

9.  Academic Performance

10. Study Load

11. Teacher Student Relationship

12. Future Career Concerns

13. Extra Cirricular Activities

14. Bullying

15. [**Stress Level**]{.smallcaps} outcome[]

## What does science say about the correlation of sleep and stress?

Not getting enough sleep can cause a negative mood, low energy,
difficulty concentrating, and a general inability to function as usual.
Lack of sleep may have severe consequences in some circumstances, such
as if a person is driving or operating heavy machinery when tired. The
occasional night of poor sleep is unlikely to cause harm, but persistent
sleep deprivation can increase the risk of several chronic health
conditions.[[1](https://www.medicalnewstoday.com/articles/322994#reducing-stress)]

Research suggests that the relationship between sleep and mental health
is complex. While lack of sleep has long been known to be a consequence
of many psychiatric conditions, more recent views suggest that lack of
sleep can also play a causal role in both the development and
maintenance of different mental health
problems.[[2](https://www.verywellmind.com/how-sleep-affects-mental-health-4783067)]

# DAG Analysis

From our data-set:

```{r ImportData}
ssdata <- read_csv("R:/Sem V/Comp Methods For Econ/Assignment-II/Data/StressLevelDataset.csv")
colnames(ssdata)<-tolower(gsub(" ","_",colnames(ssdata)))
head(ssdata)
```

## Deciding the DAG edges

```{r}
library(dagitty)
library(ggdag)
library(ggplot2)

dag<-dagify(
  STRESS ~ ANXIETY + SELF_ESTEEM + DEPRESSION + HEADACHE + SLEEP_QUALITY + BASIC_NEEDS + STUDY_LOAD + TEACHER_STUDENT_RELATION + FUTURE_CAREER_CONCERNS + BULLYING +LIVING_CONDITIONS,
  SLEEP_QUALITY ~ ANXIETY + HEADACHE + STUDY_LOAD + EXTRACIRRICULAR,
  ANXIETY ~ SELF_ESTEEM + MENTAL_HEALTH_HISTORY  + BULLYING,
  DEPRESSION ~ MENTAL_HEALTH_HISTORY+ACADEMIC_PERFORMANCE + STUDY_LOAD + FUTURE_CAREER_CONCERNS + BULLYING,
  ACADEMIC_PERFORMANCE ~ STUDY_LOAD+TEACHER_STUDENT_RELATION,

  exposure = "SLEEP_QUALITY",
  outcome = "STRESS",
  labels = c(STRESS="STRESS",
           ANXIETY="ANXIETY",
           SELF_ESTEEM="SELF_ESTEEM",
           MENTAL_HEALTH_HISTORY="MENTAL_HEALTH_HISTORY",
           DEPRESSION="DEPRESSION",
           HEADACHE="HEADACHE",
           SLEEP_QUALITY="SLEEP_QUALITY",
           BASIC_NEEDS="BASIC_NEEDS",
           ACADEMIC_PERFORMANCE="ACADEMIC_PERFORMANCE",
           STUDY_LOAD="STUDY_LOAD",
           TEACHER_STUDENT_RELATION="TEACHER_STUDENT_RELATION",
           FUTURE_CAREER_CONCERNS="FUTURE_CAREER_CONCERNS",
           EXTRACIRRICULAR="EXTRACIRRICULAR",
           BULLYING="BULLYING",
           LIVING_CONDITIONS="LIVING_CONDITIONS"
           )
)
```

```{r fig.width=10, fig.height=8}
  ggdag_status(dag,text = FALSE)+
    geom_dag_label_repel(aes(label = label), colour = "black", show.legend = FALSE)+
    geom_dag_edges_arc(edge_color = "red", curvature = 0) +
    theme_dag()

```

The backdoors are:(confounders)

```{r}
adjustmentSets(dag)
```

```{r fig.width=10,fig.height=8}
ggdag_adjustment_set(dag,shadow = TRUE,text=FALSE) + geom_dag_label_repel(aes(label = label), colour = "black", show.legend = FALSE)+theme_dag()
```

```{r fig.width=10,fig.height=8}
ggdag_collider(dag,text=FALSE) + geom_dag_label_repel(aes(label = label), colour = "black", show.legend = FALSE)+theme_dag()
```

Therefore after blocking the confounders and the colliders we need to
match on the following covariates: `SELF_ESTEEM`, `BASIC_NEEDS`,
`FUTURE_CAREER_CONCERNS`, `BULLYING`,`LIVING CONDITIONS`

# Checking the distribution of covariates for control and Treatment

To check for the effects of Sleep duration on stress, we need to set
some thresholds on sleep duration.

```{r}
print(mean(ssdata$sleep_quality))
print(median(ssdata$sleep_quality))
```

So we categorize sleep into 2 categories: - good: \>2.5hrs - bad:
\<=2.5hrs

## t-test for covariates and outcome:

The p-value estimates for the covariates in the whole data set are:

1.  Self Esteem:

```{r}
print(t.test(ssdata$self_esteem[ssdata$sleep_quality>2.5],ssdata$self_esteem[ssdata$sleep_quality<=2.5])$p.value)
```

2.  Basic Needs:

```{r}
print(t.test(ssdata$basic_needs[ssdata$sleep_quality>2.5],ssdata$basic_needs[ssdata$sleep_quality<=2.5])$p.value)
```

3.  Future Career Concerns:

```{r}
print(t.test(ssdata$future_career_concerns[ssdata$sleep_quality>2.5],ssdata$future_career_concerns[ssdata$sleep_quality<=2.5])$p.value)
```

4.  BUllying:

```{r}
print(t.test(ssdata$bullying[ssdata$sleep_quality>2.5],ssdata$bullying[ssdata$sleep_quality<=2.5])$p.value)
```

5.  Living Conditions

```{r}
print(t.test(ssdata$living_conditions[ssdata$sleep_quality>2.5],ssdata$living_conditions[ssdata$sleep_quality<=2.5])$p.value)
```

## Plotting the results:

**Factoring the treatment**

```{r}
ssdata$sleep_quality_treatment<-ifelse(ssdata$sleep_quality>2.5,1,0)
```

Plots:

```{r}
ggplot(ssdata, aes(x = ssdata$self_esteem, fill = factor(ssdata$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Self Esteem, by group") +
    scale_x_continuous(name = "Self Esteem") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(ssdata, aes(x = ssdata$basic_needs, fill = factor(ssdata$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Basic Needs, by group") +
    scale_x_continuous(name = "Basic Needs") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(ssdata, aes(x = ssdata$future_career_concerns, fill = factor(ssdata$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Future Concerns, by group") +
    scale_x_continuous(name = "Future Concerns") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(ssdata, aes(x = ssdata$bullying, fill = factor(ssdata$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Bullying, by group") +
    scale_x_continuous(name = "Bullying") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(ssdata, aes(x = ssdata$living_conditions, fill = factor(ssdata$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Living Conditions, by group") +
    scale_x_continuous(name = "Living Conditions") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

***Findings:*** We find that there is a variation in covariates which
needs to be mathced in order to properly uncerstand the causal effect of
treatment on the outcome.(extremely low p-values)

# Matching

```{r}
formula<-sleep_quality_treatment ~ self_esteem + basic_needs + future_career_concerns + bullying + living_conditions
```

```{r}
regmodel<- glm(sleep_quality_treatment ~ self_esteem + basic_needs + future_career_concerns + bullying + living_conditions,data=ssdata,family="binomial")
ssdata$propscore<-predict(regmodel,newdata=ssdata,type="response")
head(ssdata$propscore)
```

## Nearest Neighbour:(without replacement)

```{r}
library(MatchIt)
m_without_replacement = matchit(sleep_quality_treatment ~ self_esteem + basic_needs + future_career_concerns + bullying + living_conditions, method = "nearest", data = ssdata)
m_without_replacement_df<-match.data(m_without_replacement)
summary(m_without_replacement)
```

## Nearest Neighbour: (With replacement)

```{r}
m_with_replacement = matchit(sleep_quality_treatment ~ self_esteem + basic_needs + future_career_concerns + bullying + living_conditions, method = "nearest", data = ssdata,replace=TRUE)
m_with_replacement_df<-match.data(m_with_replacement)
summary(m_with_replacement)
```

## Nearest Neighbour method: (With replacement and caliper)

```{r}
m_caliper = matchit(sleep_quality_treatment ~ self_esteem + basic_needs + future_career_concerns + bullying + living_conditions, method = "nearest", data = ssdata,replace=TRUE,caliper=0.03)
m_caliper_df<-match.data(m_with_replacement)
summary(m_caliper)
```

# Post Match Plotting:

## without replacement:

### t-tests:

1.  Self Esteem:

```{r}
print(t.test(m_without_replacement_df$self_esteem[m_without_replacement_df$sleep_quality>2.5],m_without_replacement_df$self_esteem[m_without_replacement_df$sleep_quality<=2.5])$p.value)
```

2.  Basic Needs:

```{r}
print(t.test(m_without_replacement_df$basic_needs[m_without_replacement_df$sleep_quality>2.5],m_without_replacement_df$basic_needs[m_without_replacement_df$sleep_quality<=2.5])$p.value)
```

3.  Future Career Concerns:

```{r}
print(t.test(m_without_replacement_df$future_career_concerns[m_without_replacement_df$sleep_quality>2.5],m_without_replacement_df$future_career_concerns[m_without_replacement_df$sleep_quality<=2.5])$p.value)
```

4.  BUllying:

```{r}
print(t.test(m_without_replacement_df$bullying[m_without_replacement_df$sleep_quality>2.5],m_without_replacement_df$bullying[m_without_replacement_df$sleep_quality<=2.5])$p.value)
```

5.  Living Conditions

```{r}
print(t.test(m_without_replacement_df$living_conditions[m_without_replacement_df$sleep_quality>2.5],m_without_replacement_df$living_conditions[m_without_replacement_df$sleep_quality<=2.5])$p.value)
```

```{r}
ggplot(m_without_replacement_df, aes(x = m_without_replacement_df$self_esteem, fill = factor(m_without_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Self Esteem, by group[Matched]") +
    scale_x_continuous(name = "Self Esteem") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_without_replacement_df, aes(x = m_without_replacement_df$basic_needs, fill = factor(m_without_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Basic Needs, by group[Matched]") +
    scale_x_continuous(name = "Basic Needs") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_without_replacement_df, aes(x = m_without_replacement_df$future_career_concerns, fill = factor(m_without_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot ofFuture Concerns, by group[Matched]") +
    scale_x_continuous(name = "Future Concerns") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_without_replacement_df, aes(x = m_without_replacement_df$bullying, fill = factor(m_without_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Bullying, by group[Matched]") +
    scale_x_continuous(name = "Bullying") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_without_replacement_df, aes(x = m_without_replacement_df$living_conditions, fill = factor(m_without_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Living Conditions, by group[Matched]") +
    scale_x_continuous(name = "Living Conditions") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - SleepQ>2.5"))

```

## with replacement

### t-tests:

1.  Self Esteem:

```{r}
print(t.test(m_with_replacement_df$self_esteem[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$self_esteem[m_with_replacement_df$sleep_quality<=2.5][1:137])$p.value)
```

2.  Basic Needs:

```{r}
print(t.test(m_with_replacement_df$basic_needs[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$basic_needs[m_with_replacement_df$sleep_quality<=2.5][1:137])$p.value)
```

3.  Future Career Concerns:

```{r}
print(t.test(m_with_replacement_df$future_career_concerns[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$future_career_concerns[m_with_replacement_df$sleep_quality<=2.5][1:137])$p.value)
```

4.  BUllying:

```{r}
print(t.test(m_with_replacement_df$bullying[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$bullying[m_with_replacement_df$sleep_quality<=2.5][1:137])$p.value)
```

5.  Living Conditions

```{r}
print(t.test(m_with_replacement_df$living_conditions[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$living_conditions[m_with_replacement_df$sleep_quality<=2.5][1:137])$p.value)
```

```{r}
ggplot(m_with_replacement_df, aes(x = m_with_replacement_df$self_esteem, fill = factor(m_with_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Self Esteem, by group[Matched]") +
    scale_x_continuous(name = "Self Esteem") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_with_replacement_df, aes(x = m_with_replacement_df$basic_needs, fill = factor(m_with_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Basic Needs, by group[Matched]") +
    scale_x_continuous(name = "Basic Needs") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_with_replacement_df, aes(x = m_with_replacement_df$future_career_concerns, fill = factor(m_with_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot ofFuture Concerns, by group[Matched]") +
    scale_x_continuous(name = "Future Concerns") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_with_replacement_df, aes(x = m_with_replacement_df$bullying, fill = factor(m_with_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Bullying, by group[Matched]") +
    scale_x_continuous(name = "Bullying") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_with_replacement_df, aes(x = m_with_replacement_df$living_conditions, fill = factor(m_with_replacement_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Living Conditions, by group[Matched]") +
    scale_x_continuous(name = "Living Conditions") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - SleepQ>2.5"))
```

## with caliper

### t-tests:

1.  Self Esteem:

```{r}
print(t.test(m_caliper_df$self_esteem[m_caliper_df$sleep_quality>2.5][1:137],m_caliper_df$self_esteem[m_caliper_df$sleep_quality<=2.5][1:137])$p.value)
```

2.  Basic Needs:

```{r}
print(t.test(m_caliper_df$basic_needs[m_caliper_df$sleep_quality>2.5][1:137],m_caliper_df$basic_needs[m_caliper_df$sleep_quality<=2.5][1:137])$p.value)
```

3.  Future Career Concerns:

```{r}
print(t.test(m_caliper_df$future_career_concerns[m_caliper_df$sleep_quality>2.5],m_caliper_df$future_career_concerns[m_caliper_df$sleep_quality<=2.5])$p.value)
```

4.  BUllying:

```{r}
print(t.test(m_caliper_df$bullying[m_caliper_df$sleep_quality>2.5],m_caliper_df$bullying[m_caliper_df$sleep_quality<=2.5])$p.value)
```

5.  Living Conditions

```{r}
print(t.test(m_caliper_df$living_conditions[m_caliper_df$sleep_quality>2.5],m_caliper_df$living_conditions[m_caliper_df$sleep_quality<=2.5])$p.value)
```

```{r}
ggplot(m_caliper_df, aes(x = m_caliper_df$self_esteem, fill = factor(m_caliper_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Self Esteem, by group[Matched]") +
    scale_x_continuous(name = "Self Esteem") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_caliper_df, aes(x = m_caliper_df$basic_needs, fill = factor(m_caliper_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Basic Needs, by group[Matched]") +
    scale_x_continuous(name = "Basic Needs") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_caliper_df, aes(x = m_caliper_df$future_career_concerns, fill = factor(m_caliper_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot ofFuture Concerns, by group[Matched]") +
    scale_x_continuous(name = "Future Concerns") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_caliper_df, aes(x = m_caliper_df$bullying, fill = factor(m_caliper_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Bullying, by group[Matched]") +
    scale_x_continuous(name = "Bullying") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - Sleep>2.5"))
```

```{r}
ggplot(m_caliper_df, aes(x = m_caliper_df$living_conditions, fill = factor(m_caliper_df$sleep_quality_treatment))) + geom_density(position="identity", alpha=0.6) +
    scale_fill_brewer(palette="Dark2") + ggtitle("Density plot of Living Conditions, by group[Matched]") +
    scale_x_continuous(name = "Living Conditions") +
    scale_y_continuous(name = "Density") + theme(plot.title = element_text(size = 14, face =
                                                                               "bold"), text = element_text(size = 12)) + guides(fill=guide_legend(title=NULL))+
    scale_fill_discrete(labels=c("Control - SleepQ<=2.5", "Treatment - SleepQ>2.5"))
```

# ATE

## without replacement

```{r}
t.test(m_without_replacement_df$stress_level[m_without_replacement_df$sleep_quality>2.5][1:137],m_without_replacement_df$stress_level[m_without_replacement_df$sleep_quality<=2.5][1:137])
```

```{r}
model_ate_no_repl <- lm(stress_level~sleep_quality_treatment,data=m_without_replacement_df)
summary(model_ate_no_repl)
```

We see the treatment group : people with sleep quality \>2.5 have a mean
stress level of 0.45 and the control group has a mean stress level of
1.6, which is significantly high. Also the intercept in 1.1 units lower
for our treatment group.

## with replacement

```{r}
t.test(m_with_replacement_df$stress_level[m_with_replacement_df$sleep_quality>2.5][1:137],m_with_replacement_df$stress_level[m_with_replacement_df$sleep_quality<=2.5][1:137])
```

```{r}
model_ate_repl <- lm(stress_level~sleep_quality_treatment,data=m_with_replacement_df)
summary(model_ate_repl)
```

We see the treatment group : people with sleep quality \>2.5 have a mean
stress level of 0.45 and the control group has a mean stress level of
1.1, which is significantly high. Also the intercept in 0.6 units lower
for our treatment group.

## with caliper

```{r}
t.test(m_caliper_df$stress_level[m_caliper_df$sleep_quality>2.5][1:137],m_caliper_df$stress_level[m_caliper_df$sleep_quality<=2.5][1:137])
```

```{r}
model_ate_caliper <- lm(stress_level~sleep_quality_treatment,data=m_caliper_df)
summary(model_ate_caliper)
```

We see the treatment group : people with sleep quality \>2.5 have a mean
stress level of 0.45 and the control group has a mean stress level of 1,
which is significantly high. Also the intercept in 0.6 units lower for
our treatment group.

# Conclusion

From the above analysis we can show that sleep does causally affect
stress levels. Lower sleep quality causes higher stress levels.
